---
title: "Kaset Data Science Project"
author: "Sawangpong Muadphet"
date: "7/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Kaset Project 

install package

```{r}

install.packages("ggplot2")
install.packages('scales')
```

library(ggplot2)
library(scales)

setwd("~/KasetApp/R")
```

## ReadData 

```{r}
do2 <- read.csv(file='../exports/do2.csv')
do5 <- read.csv(file='../exports/do2.csv')
ec1 <- read.csv(file='../exports/ec1.csv')
ec2 <- read.csv(file='../exports/ec2.csv')
ec3 <- read.csv(file='../exports/ec3.csv')
ec4 <- read.csv(file='../exports/ec4.csv')
ec5 <- read.csv(file='../exports/ec5.csv')
ec6 <- read.csv(file='../exports/ec6.csv')
```

## Summary
```{r}
summary(do2)
summary(do5)
summary(ec1)
summary(ec2)
summary(ec3)
summary(ec4)
summary(ec5)
summary(ec6)
```

## Plot

```{r}
do2_plot <- ggplot(do2,aes(y = value, x = ts)) + geom_point() 
do2_plot
```

```{r}
do5_plot <- ggplot() + geom_point(aes(y = value, x = ts),data = do5)
do5_plot
```

```{r}
ec1_plot <- ggplot() + geom_point(aes(y = value, x = ts),data = ec1)+ scale_x_datetime(breaks = date_breaks("4 sec"), labels = date_format("%M:%S"))
ec1_plot
```
